\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation

### 2018-05-06 ccs/pipe.tex
changes, comments

\vspace{-0.1in}
\section{Secure code partitioning}
\label{sec:pipe}

@@

We  now describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits.
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). More formal details follow, while an example illustrating the technique of secure code partitioning is provided in  \appendixref{codepartitioning}.

@@

To overcome this problem, we define a sequence of new programs
$\progn_i$ ($1\leq i\leq k$) as follows. Once again, define $\stateq_0
= \bot$. Without
loss of generality, let all $\stateq_i$ be values in some additive ring
$(\mathbb{Z},+)$ (e.g., the additive ring $(\mathbb{Z}_{2^{64}},+)$,
i.e., the additive ring of integers modulo $2^{64}$).
Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from
the same ring $(\mathbb{Z},+)$ by Alice (in our implementation, all
$r_i$ values are generated by a pseudorandom function). Let $\progn_1$
be the program that takes as input $x,r_1$ from Alice and $y$ from Bob
(and empty state $\stateq_0$), and runs $\prog_1$ (as defined above) to
compute $\stateq_1$ and then outputs $o_1 = \stateq_1 + r_1$ {\em only
  to} Bob\footnote{While the description of our protocol here assumes
  that
  the underlying backend supports only one party receiving output,
  this is only a simplifying assumption, and we can easily modify our
  protocol in the case where both parties must receive the same
  output. %To do so, we modify $\progn_1$ to output $o_1 = s_1+r_1+r'_1$ to
  %both parties (where $r'_1$ is random and chosen by Bob). We can then
  %appropriately modify the remaining steps as well.
  }. 
  Alice's output
from $\progn_1$ is $r_1$. Next, every $\progn_i$ ($2\leq i\leq k-1$)
takes as inputs $x,r_{i-1},r_i$ from Alice and $y,o_{i-1}$ from Bob,
runs $\prog_i$
on inputs $x,y$ and state $\stateq_{i-1} = (o_{i-1}-r_{i-1})$ (where $-$ denotes
subtraction in the ring $(\mathbb{Z},+)$) and then outputs $\stateq_i+r_i$
to Bob and $r_i$ to Alice. The last
program $\progn_k$ takes inputs $x,y,r_{k-1},o_{k-1}$, runs $\prog_k$
on inputs $x,y$ and state $\stateq_{k-1} = (o_{k-1}-r_{k-1})$ and outputs $z$ to both
parties.

@@

%\begin{theorem}[Correctness and security of partitioning]
%Let $\prog$ be a program in our source language with output $z$, that
%is decomposed into programs
%$\prog'_1\seq\prog'_2\seq\dots\seq\prog'_k$ (as defined in
%the partioning procedure above) and compiled into the protocol $\prot
%= \prot_1\seq\prot_2\dots\seq\prot_k$ that outputs $r_1\seq
%r_2\seq\dots\seq z$ 
%(to Alice) and $o_1\seq o_2\seq\dots||z$ (to Bob), then $\prot$ securely
%realizes $P$.
%\end{theorem}
%
%\noindent {\em Proof.} From \theoremref{security}, it follows that
%$\prot_i$ securely realizes $\prog'_i$ for every $1\leq i\leq
%k$. Hence, we know that the only information learnt by Alice is
%$r_1||r_2||\cdots||r_{k-1}||z$ and by Bob is
%$o_1||o_2||\cdots||o_{k-1}||z$. Since $r_i$ and $o_i$ ($1\leq i\leq
%k-1$) are individually uniformly random (in $(\mathbb{Z},+)$, outputs
%received by the adversary can be easily simulated given the final
%output $z$.
\vspace{-0.1in}
\paragraph{Implementing code partitioning.}
We use partitioning for programs that require large
circuits. Specifically, the programmer decomposes the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$ manually. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the manual decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave
the construction of such an analysis as future work.% \nc{I changed the heading.}

>>>>

%\vspace{-0.1in}
\section{Secure code partitioning}
\label{sec:pipe}

@@

We  now describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits.
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). 
\dg{Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
}
More formal details follow, while an example illustrating the technique of secure code partitioning is provided in  \appendixref{codepartitioning}. \dg{We describe it only in the arithmetic setting but the same can be done in the Boolean setting as well.}

@@

To overcome this problem, we define a sequence of new programs
$\progn_i$ ($1\leq i\leq k$) as follows. Once again, define $\stateq_0
= \bot$. Without
loss of generality, let all $\stateq_i$ be values in some additive ring
$(\mathbb{Z},+)$ (e.g., the additive ring $(\mathbb{Z}_{2^{64}},+)$,
i.e., the additive ring of integers modulo $2^{64}$).
Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from
the same ring $(\mathbb{Z},+)$ by Alice (in our implementation, all
$r_i$ values are generated by a pseudorandom function). Let $\progn_1$
be the program that takes as input $x,r_1$ from Alice and $y$ from Bob
(and empty state $\stateq_0$), and runs $\prog_1$ (as defined above) to
compute $\stateq_1$ and then outputs $o_1 = \stateq_1 + r_1$ {\em only
  to} Bob\footnote{While the description of the scheme here assumes
  that
  the underlying backend supports only one party receiving output,
  this is only a simplifying assumption, and we can easily modify our
  protocol in the case where both parties must receive the same
  output. %To do so, we modify $\progn_1$ to output $o_1 = s_1+r_1+r'_1$ to
  %both parties (where $r'_1$ is random and chosen by Bob). We can then
  %appropriately modify the remaining steps as well.
  }. 
  Alice's output
from $\progn_1$ is $r_1$. Next, every $\progn_i$ ($2\leq i\leq k-1$)
takes as inputs $x,r_{i-1},r_i$ from Alice and $y,o_{i-1}$ from Bob,
runs $\prog_i$
on inputs $x,y$ and state $\stateq_{i-1} = (o_{i-1}-r_{i-1})$ (where $-$ denotes
subtraction in the ring $(\mathbb{Z},+)$) and then outputs $\stateq_i+r_i$
to Bob and $r_i$ to Alice. The last
program $\progn_k$ takes inputs $x,y,r_{k-1},o_{k-1}$, runs $\prog_k$
on inputs $x,y$ and state $\stateq_{k-1} = (o_{k-1}-r_{k-1})$ and outputs $z$ to both
parties.

@@

%\begin{theorem}[Correctness and security of partitioning]
%Let $\prog$ be a program in our source language with output $z$, that
%is decomposed into programs
%$\prog'_1\seq\prog'_2\seq\dots\seq\prog'_k$ (as defined in
%the partioning procedure above) and compiled into the protocol $\prot
%= \prot_1\seq\prot_2\dots\seq\prot_k$ that outputs $r_1\seq
%r_2\seq\dots\seq z$ 
%(to Alice) and $o_1\seq o_2\seq\dots||z$ (to Bob), then $\prot$ securely
%realizes $P$.
%\end{theorem}
%
%\noindent {\em Proof.} From \theoremref{security}, it follows that
%$\prot_i$ securely realizes $\prog'_i$ for every $1\leq i\leq
%k$. Hence, we know that the only information learnt by Alice is
%$r_1||r_2||\cdots||r_{k-1}||z$ and by Bob is
%$o_1||o_2||\cdots||o_{k-1}||z$. Since $r_i$ and $o_i$ ($1\leq i\leq
%k-1$) are individually uniformly random (in $(\mathbb{Z},+)$, outputs
%received by the adversary can be easily simulated given the final
%output $z$.

\paragraph{Implementing code partitioning.}
We use partitioning for programs that require large
circuits. Specifically, we first decompose the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
\dg{Automating the  decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program.
Resource analysis of programs is a well-known hard problem~\cite{raml}
 and we describe a heuristic analysis in Appendix~\ref{app:pipe-idea}.}
% \nc{I changed the heading.}

### 2018-05-06 ccs/related.tex
changes, comments

\vspace{-0.2in}
\section{Related work}
\label{sec:related}

@@

\mpc backends  have made  tremendous progress in the last decade.
For example, the circuits can be optimized for depth~\cite{ddkssz15,cbmcgcdepth}, large garbled circuits can be pipelined~\cite{yao-pipe}, and oblivious RAM~\cite{oram1,oram2} can be used to hide access patterns of MIPS code~\cite{mips}. Incorporating these backends would only improve the performance and scalability of \tool implementations.

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This requires deep knowledge of cryptography
to ensure security.
Examples include classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, sequence analysis~\cite{franz}, biometric identification~\cite{huang}, matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees/forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.
% As seen from our experiments, the protocols generated by \tool give us better or comparable execution times as many of the above works with minimal programmer overhead. %\nc{What do we want to say here exactly?}

>>>>

\section{Related work}
\label{sec:related}

@@

\mpc backends  have made  tremendous progress in the last decade.
For example, the circuits can be optimized for depth~\cite{ddkssz15,cbmcgcdepth}, large garbled circuits can be pipelined~\cite{yao-pipe,oblivm}, and oblivious RAM~\cite{oram1,oram2} can be used to hide access patterns of MIPS code~\cite{mips}. Incorporating these backends would only improve the performance and scalability of \tool implementations.

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This requires deep knowledge of cryptography
to ensure security.
Examples include classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, sequence analysis~\cite{franz}, biometric identification~\cite{huang}, matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees/forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.

\TODO{add Groce et al., Mood et al. Lindell's Libscapi, Chameleon, Gazelle, SPDZ. Reviewers want citations for  3PC papers also. May be we can say they are not 2PC?}
% As seen from our experiments, the protocols generated by \tool give us better or comparable execution times as many of the above works with minimal programmer overhead. %\nc{What do we want to say here exactly?}
